The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-01-26 repeater-vladata.tex
incorporated comments from geoff, uk, shami

\title{The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population}
%\title{Multi-Telescope Burst Properties and Implications for FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

\author[0000-0002-4119-9963]{C.~J.~Law}
\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}

@@

\author{T.~Cantwell}
\affiliation{University of Manchester, UK}

\author{S.~H.~Carey}
\affiliation{University of Cambridge, UK}

@@

\author{K.~Grainge}
\affiliation{University of Manchester, UK}

@@

\author{J.~Hickish}
\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
\affiliation{University of Cambridge, UK}

\author{R.~Fender}
\affiliation{University of Oxford, UK}

@@

\author{K.~Mooley}
\affiliation{University of Oxford, UK}

@@

\author{Y.~C.~Perrott}
\affiliation{University of Cambridge, UK}

@@

\author{N.~Razavi-Ghods}
\affiliation{University of Cambridge, UK}

@@

\author{A.~Scaife}
\affiliation{University of Manchester, UK}

@@

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure. We present the burst energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

\section{Introduction}
Fast Radio Bursts (FRBs) are a new class of millisecond-duration radio transient with a dispersion measure (DM) that implies that they originate outside of our Galaxy. At extragalactic (and potentially cosmological) distances, they are not only unusually luminous, but they provide a new tracer of other galaxies and the intergalactic medium (IGM). In this way, FRBs have opened a whole new playground in astrophysics \citep[e.g.,][]{2014A&A...562A.137F, 2014ApJ...780L..33M, 2016MNRAS.457..232C}. However, that potential has been hamstrung by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series that presents the first localization and unambiguous identification of an FRB host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec. Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 \citep{OPT, EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc \citep{2016A&A...594A..13P}, which are orders of magnitude larger than any other millisecond transient. This shows that FRBs are more energetic than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy. The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.

The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole. However, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with several statistical tests we can use to test this connection.

We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible. Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}. The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission. FRB repetition also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

Given that FRBs are now known to be useful probes of the IGM, there is even more motivation to make new detections and localizations. The relatively faint counterpart to \frb\ argues that direct localization of the radio burst will continue to be the best way to find optical hosts to measure distances. Our multi-telescope constraints on burst spectra, measurement of host properties, burst rate estimates, and other properties will inform new strategies for finding FRBs.

@@

\subsection{VLA}
The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo. We concluded with a new, 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration. In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which include all nine burst detections.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}. To maximize sensitivity, the channel frequency width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each.

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on existing, CPU-based hardware of the VLA correlator backend with transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}. Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 554--560 pc cm$^{-3}$. Gain calibration is read from the ''telcal'' system, which uses phase-only calibration on the previous gain calibrator. A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.

Burst detections and localizations were made within hours of data being recorded. The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ''quasi real-time''. For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image. Summary statistics are saved for images with S/N higher than 6.4, which captures the tail of the thermal noise distribution without adding significant computational or data volume burden. Each image with a pixel with S/N higher than 7.4 is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum. More detailed analysis, including improved calibration and localization, is conducted offline.

Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}. Time cut-out visibility data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}. Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

@@

During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz. We recorded total full Stokes polarization intensity spectra with time at a resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing. The ull width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

@@

\subsection{AMI}

@@

We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts. Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location. Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger. We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy. Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio ''afterglow'' (on $\sim$days timescale) signal from the FRB. This limit is close to the flux density measured by the VLA \citep{LOC}.

@@

\subsection{Multi-Telescope Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA (Figure \ref{fig:multi}). Of these, the burst on 57648 was detected by Arecibo at the same time (after correcting for the known DM of \frb). The Arecibo detection of this burst had a significance of {\color{red} xx$\sigma$ (Jason)}.

@@

This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts emit over more than an octave of frequency. However, this is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width. However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely. However, as described in \S \ref{sec:spec}, some of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.

@@

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{lccccccc}
\hline
Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
57623               & 258             & 38        & 7.8  & 562.5 & 0.46 & 2.8 & 300 \\
57633.68            & 2000            & 179       & 65   & 561.4 & 2.20 & 3.2 & 520 \\
57633.70\tablenotemark{a} & 105       & 15        & 5.9  & 555.4 & $>$0.32 & $<$2.5 & $>$320 \\
57638               & 65              & 12        & 1.8  & 554.9 & 0.07 & 3.1 & 440 \\
57643               & 375             & 100       & 13   & 559.3 & 0.44 & 2.8 & 530 \\
57645               & 38              & 13        & 2.6  & 554.1 & 0.05 & 2.7 & 970 \\
57646\tablenotemark{a} & 69           & 20        & 3.9  & 568.1 & $>$0.19 & $<$2.5 & $>$360 \\
57648\tablenotemark{b} & 97           & 25        & 2.9  & 557.8 & 0.11 & 2.8 & 440 \\
57649               & 110             & 36        & 6.3  & 559.9 & 0.08 & 2.9 & 1400 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

@@

The burst spectra are generally characterized by a broad, Gaussian shape with strong inter-channel modulation. We fit a Gaussian shape to each burst to estimate its characteristic width and peak flux (Table \ref{tab:spec}). The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution. This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
% TODO: fit with generative model with 100% amplitude modulations (emcee?)

All but two of the best-fit Gaussians are centered inside the 3~GHz band and most appear contained by the 1~GHz wide band. This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}. A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.

@@

@@

@@

\subsubsection{Circular Polarization}
The VLA S-band recievers natively measure circular polarization, although for observing efficiency we chose not include polarization calibration procedures. Crude constraints on circular polarization are possible by comparing the burst intensity in right and left-hand polarized data products. The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%. \frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo). Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.

\subsection{Temporal Statistics}
\label{sec:temp}
Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102. In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing. The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary. Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit). The mean detection rate for the last part of the campaign was $\rm{R}=0.3$\ hour$^{-1}$.

There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign. We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$. By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence. This weak constraint is consistent with the broader trend seen by the VLA and Arecibo.

@@

During the August--September 2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence. We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales. The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also]{2011MNRAS.417.1871P}. 
The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data. We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach. However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches][]{2007ApJ...663..497C, 2013Natur.497..591A}

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). The VLA has also shown for the first time that many bursts are contained within the 3~GHz band. For those bursts, the mean S-band flux density can be converted to an energy with no assumptions about its spectral properties.

>>>>

\title{The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population}
%\title{Multi-Telescope Burst Properties and Implications for FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

\author[0000-0002-4119-9963]{C.~J.~Law}
\affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}

@@

\author{T.~Cantwell}
\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}

\author{S.~H.~Carey}
\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}

@@

\author{K.~Grainge}
\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}

@@

\author{J.~Hickish}
\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}

\author{R.~Fender}
\affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}

@@

\author{K.~Mooley}
\affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}

@@

\author{Y.~C.~Perrott}
\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}

@@

\author{N.~Razavi-Ghods}
\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}

@@

\author{A.~Scaife}
\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}

@@

\author{P.~K.~G.~Williams}
\affiliation{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA, USA}

\begin{abstract}
The recent precision localization of \frb\ has helped identify its host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source. We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz. We show that the burst spectra typically have a broad shape that tapers off on scales of $\sim500$~MHz, plus fine spectral structure on MHz-frequency scales. We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. **This source shows that optimal FRB survey strategies should...**
\end{abstract}

\section{Introduction}
Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}. Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}. Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}. However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.

This paper is part of a series that presents the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}. This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}. The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.

The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole. If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies. However, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible. Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}. The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

This paper opens by describing the multi-telescope observing campaign and a refined analysis of the nine VLA bursts. Next, we present the spectrum of a burst from \frb\ that was simultaneously detected by the VLA and Arecibo observatories. **Simulations of temporal statistics and luminosity distribution...** **New estimate of FRB rate and comparison to other transient populations** We close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.

@@

\subsection{VLA}
The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo. We concluded with a 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration. In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which include all nine burst detections and is the widest bandwidth to have ever detected an FRB.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The channel frequency width was set to maximize sensitivity to the known DM of \frb, with the largest total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each.

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on existing, CPU-based hardware of the VLA correlator backend with transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}. Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$. Gain calibration was made from observations of J0555+3948 by the ''telcal'' system, which uses phase-only calibration. A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.

Burst detections and localizations were made within hours of data being recorded. The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ''quasi real-time''. For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image. We empirically identified S/N thresholds of 6.4 and 7.4 as useful to capture data quality statistics and candidates for inspection, respectively. The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum. All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.

Computational notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}. Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}. Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

@@

During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz. We recorded total full Stokes polarization intensity spectra with time at a resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing. The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

@@

\subsection{AMI-LA}

@@

We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1s samples at and in the vicinity of the detected bursts. Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location. Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger. We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy. Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB. This limit is similar to the flux density measured by the VLA \citep{LOC}.

@@

\subsection{Multi-Observatory Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA (Figure \ref{fig:multi}). Of these, the burst on 57648 was detected by Arecibo at the same time (after correcting for the known DM of \frb). The Arecibo detection of this burst had a significance of {\color{red} xx$\sigma$ (Jason)}.

@@

This simultaneous detection of a burst from roughly 1.2 to 3.5~GHz shows that some bursts emit over more than an octave of frequency. However, the other three...**
**
 is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width. However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely. However, as described in \S \ref{sec:spec}, some of the VLA bursts peak within the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.

@@

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). Table \ref{tab:spec} shows the optimal image integrated flux density, image S/N, and Stokes V using this new scheme. Improved burst spectral parameters are also measured from MCMC modeling of the dynamic spectra.

\begin{table*}
\caption{Properties of Bursts from \frb}
\centering
\begin{tabular}{lcccccccc}
\hline
Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
57623.74402686      & 258             & 38        & 7.8  & 562.5 & 460 & 2.8 & 300 & --2 \\
57633.67986367      & 2000            & 179       & 65   & 561.4 & 2200 & 3.2 & 520 & --44 \\
57633.69515938\tablenotemark{a} & 105       & 15        & 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +9 \\
57638.49937435      & 65              & 12        & 1.8  & 554.9 & 70 & 3.1 & 440 & +4 \\
57643.45730263      & 375             & 100       & 13   & 559.3 & 440 & 2.8 & 530 & +9 \\
57645.42958602      & 38              & 13        & 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
57646.46600650\tablenotemark{a} & 69           & 20        & 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +3 \\
57648.43691490\tablenotemark{b} & 97           & 25        & 2.9  & 557.8 & 110 & 2.8 & 440 & +7 \\
57649.45175697      & 110             & 36        & 6.3  & 559.9 & 80 & 2.9 & 1400 & --1 \\ \hline
\end{tabular}
\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
\label{tab:spec}
\end{table*}

@@

The burst spectra are generally characterized by a broad, Gaussian shape with strong inter-channel modulation. We fit a Gaussian shape to each burst to estimate its characteristic width and peak flux (Table \ref{tab:spec}). There is strong structure on smaller scales with channel-to-channel modulation is as high as 100\% (see \S \ref{sec:auto}). This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
% TODO: fit with generative model with 100% amplitude modulations (emcee?)

All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band. This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}. A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.

@@

**Does DM correlate with other spectral/flux properties?**

@@

**Does channel-scale structure only appear around 3~GHz?**

@@

\subsubsection{Circular Polarization}
The VLA S-band recievers measure circular polarization, although for observing efficiency we choose not to include polarization calibration procedures. Constraints on circular polarization are possible since the gain calibrator is a well-known polarization calibrator with little Stokes V flux. In that case, the apparent circular polarization fraction is $(RR-LL)/(RR+LL)$, which for the most significant bursts is at most 3\%. \frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo). Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.

\subsection{Temporal Statistics}
\label{sec:temp}
Geoff comments:
-- need to clarify that burst rate change is significant
-- what is "last/first part of campaign"?
-- not clear how significant nondetections are, since observational details not obvious yet

Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102. In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing. The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary. Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit). The mean detection rate for the last part of the campaign was $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.

There is weak evidence that the \frb\ burst rate decreased through the last 27 hours of the S-band campaign. We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$. By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence. This weak constraint is consistent with the broader trend of a changing rate seen on month timescales by Arecibo.

@@

During the August--September 2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence. We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales. The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also][]{2011MNRAS.417.1871P}. 
The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data. We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach. However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches;][]{2007ApJ...663..497C, 2013Natur.497..591A}

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band. If those bursts truly only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
